### 2015-03-20 appendices.tex
more grammatical fixes updates to lists in the appendix

    The SDLC often contains more than the 5 basic steps of requirements, design,
    implementation, testing, and  deployment/maintenance.  Those are the high-level
    phases, but many steps are required to complete each phase.  The following list
    provides a more detailed list of what needs to be accomplished in the 
    entire life cycle of software development. These steps do not need 
    to occur in a sequential fashion.

@@

        Some diagnostic plots for the baseline quality function
        can be seen in Figure \ref{fig:quality-diag}.  The normal probability plot,
        a.k.a. QQ Plot, shows the errors are not exactly normally distributed, but
        the baseline quality function had good predictive power as shown by the
        high $R^2$. The fitted versus
        residuals plot indicates a lack of heteroscedasticity.  
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.25]{images/quality_diag.png}
            \caption{QUALITY DIAGNOSTIC PLOTS}
            \label{fig:quality-diag}
        \end{figure}

@@

@@

    \begin{itemize}
    \item Change to Database Structure  
    \item Modify Database Data    
    \item Create a New Database, number of new databases  
    \item Server Configuration Changes Required   
    \item New Servers Required   
    \item Number of Team Members Involved  
    \item Number of (sub)Systems Involved  
    \item Estimation Date
    \item Number of Days Allowed
    \item List of Other Attributes
    \item Number of Screens Involved 
    \item Actual Value (hours, days, dollars) 
    \end{itemize}

    \begin{description}
        \item[Estimated Dev Hours] - 
            The number of development hours estimated for a 
            project, this is just developer hours
        \item[Estimated Doc Hours] - 
            The number of documentation hours estimated for a project
        \item[Estimated Test Hours] - 
            The number of testing hours estimated for a project
        \item[Estimated Deployment Hours] - 
            The number of estimated hours required to 
            deploy the project
    \end{description}

    \subsection{REQUIREMENTS}
    List of: 
    \begin{description}
      \item[Title] 
      \item[Descrition]
      \item[author]
      \item[projectID]
      \item[date]
      \item[Comments] list of \\
      \begin{description}
        \item[date]
        \item[comment Text]
        \item[author]
      \end{description}
    \end{description}

    \subsection{MAINTENANCE (DEFECTS)}
    List of:
    \begin{description}
      \item[Project] 
      \item[Release]
      \item[description]
      \item[date Entered]
      \item[Date fixed]
      \item[Comments] list of \\
      \begin{description}
        \item[date]
        \item[comment Text]
        \item[author]
      \end{description}
    \end{description}

    \subsection{TESTING}

    List of:
    \begin{description}
      \item[Project] 
      \item[Release]
      \item[title]
      \item[description]
      \item[author]
      \item[Date Started]
      \item[Date Executed]
      \item[Status (Pending, pass, fail)]
      \item[Comments] list of \\
      \begin{description}
        \item[date]
        \item[comment Text]
        \item[author]
      \end{description}
    \end{description}

@@

    List of Coding Tasks:
    \begin{description}
      \item[Project] 
      \item[Release]
      \item[List of Files]
      \item[author]
      \item[Date Started]
      \item[Completion Date]
      \item[Number of Unit Tests]
      \item[Lines of Code]
      \item[Others] See \cite{Jones2009, Jones2012, Rubin2007, Snipes2013}
    \end{description}

@@

    List of:
    \begin{description}
      \item[Project] 
      \item[Release]
      \item[date Entered]
      \item[Date Scheduled]
      \item[Date Executed]
      \item[Ordering/Prerequisites]
      \item[Comments] list of \\
      \begin{description}
        \item[date]
        \item[comment Text]
        \item[author]
      \end{description}
    \end{description}

>>>>

    The SDLC often contains more than the five basic steps of requirements, design,
    implementation, testing, and  deployment/maintenance.  Those are the high-level
    phases, but many steps are required to complete each phase.  The following list
    provides a more detailed list of what needs to be accomplished in the 
    entire life cycle of software development. These steps do not need 
    to occur in a sequential fashion.

@@

        Some diagnostic plots for the baseline quality function
        can be seen in Figure \ref{fig:quality-diag}.  The normal probability plot,
        a.k.a. Q-Q Plot, shows the errors are not exactly normally distributed, but
        the baseline quality function had good predictive power as shown by the
        high $R^2$. The fitted versus
        residuals plot indicates a lack of heteroscedasticity.  
        \begin{figure}[ht]
            \centering
            \includegraphics[scale=.25]{images/quality_diag.png}
            \caption{QUALITY DIAGNOSTIC PLOTS}
            \label{fig:quality-diag}
        \end{figure}

@@

    This appendix describes some additional SDLC attributes that could be tracked to help improve
    estimation.  The SDLC-AE could be expanded to include the following.

@@

        The following are additional data points that could be tracked for project estimation.
        \begin{easylist}[itemize]
            & Change to Database Structure  
            & Modify Database Data    
            & Create a New Database, number of new databases  
            & Server Configuration Changes Required   
            & New Servers Required   
            & Number of People Involved  
            & Number of (sub)Systems Involved  
            & Estimation Date
            & Number of Days Allowed
            & List of Other Attributes
            & Number of Screens Involved 
            & Actual Values (hours, days, dollars) 
            & Estimated Values
            && Estimated Dev Hours: 
                The number of development hours estimated for a 
                project, this is just developer hours
            && Estimated Doc Hours: 
                The number of documentation hours estimated for a project
            && Estimated Test Hours:
                The number of testing hours estimated for a project
            && Estimated Deployment Hours: 
                The number of estimated hours required to 
                deploy the project
        \end{easylist}

    \subsection{REQUIREMENTS}

        The following are additional data points that could be tracked for the requirements phase of an
        SDLC project.
        \begin{easylist}[itemize]
            & Title
            & Description
            & Author
            & Project
            & Date
            & Comments
            &&  Date
            &&  Comment text
            &&  Author
        \end{easylist}

@@

        The following are additional data points that could be tracked for the development phase of an
        SDLC project.
        \begin{easylist}[itemize]
            & Project
            & Release
            & List of files
            & Author
            & Date started
            & Completion date
            & Number of unit tests
            & Lines of code
            & Percentage of automated test coverage
            & Others
        \end{easylist}

    \subsection{TESTING}
        The following are additional data points that could be tracked during, before, and after the
        testing phase of an SDLC project.
        \begin{easylist}[itemize]
            & Project
            & Release
            & Title
            & description]
            & Author]
            & Date started
            & Date executed
            & Status (pending, pass, fail)
            & Comments 
            && Date
            && Comment text
            && Author
        \end{easylist}

@@

        The following are additional data points that could be tracked for the implementation of a project.
        \begin{easylist}[itemize]
            & Project
            & Release
            & date Entered
            & Date Scheduled
            & Date Executed
            & Ordering/Prerequisites
            & Comments
            && date
            && Comment text
            && Author
        \end{easylist}

    \subsection{MAINTENANCE (DEFECTS)}

        The following are additional data points that could be tracked for maintenance of a project.
        \begin{easylist}[itemize]
            & Project
            & Release
            & Description
            & Date Entered
            & Date fixed
            & Comments
            && Date
            && Comment text
            && Author
        \end{easylist}

### 2015-03-20 paper_10_intro.tex
more grammatical fixes updates to lists in the appendix

    Software Engineering Method and Theory (SEMAT) is claiming to 
    be the ``new software engineering'' 
    \cite{Jacobson2014}. 
    \nomenclature{SEMAT}{Software Engineering Method and Theory}
    The authors rightfully claim that 
    software engineering lacks
    an underlying theoretical foundation found in other 
    engineering disciplines.  This lack of theory
    has led software engineering to not be engineering, but 
    rather a craft.  The goal of 
    SEMAT is to merge the craftsmanship and engineering to 
    provide a foundation for software
    engineering.  The primary initiative of SEMAT 
    has been the creation of a kernel for 
    software engineering.  The kernel is the minimal set 
    of things common to all software development
    endeavours. The three parts to the kernel are:
    \begin{description}
        \item[Measurement] - There must exist a means to 
            determine the health and progress of an endeavour
        \item[Categorization]-  The activities must progress 
            through categories during an endeavour
        \item[Competencies] - Specific competencies will 
            be required for completing activities
    \end{description}

>>>>

    Software Engineering Method and Theory (SEMAT) is claiming to 
    be the ``new software engineering'' 
    \cite{Jacobson2014}. 
    \nomenclature{SEMAT}{Software Engineering Method and Theory}
    The authors rightfully claim that 
    software engineering lacks
    an underlying theoretical foundation found in other 
    engineering disciplines.  This lack of theory
    has led software engineering to not be engineering, but 
    rather a craft.  The goal of 
    SEMAT is to merge the craftsmanship and engineering to 
    provide a foundation for software
    engineering.  The primary initiative of SEMAT 
    has been the creation of a kernel for 
    software engineering.  The kernel is the minimal set 
    of things common to all software development
    endeavours. The three parts to the kernel are:
    \begin{enumerate}
        \item \textbf{Measurement} - There must exist a means to 
            determine the health and progress of an endeavour.
        \item \textbf{Categorization} -  The activities must progress 
            through categories during an endeavour.
        \item \textbf{Competencies} - Specific competencies will 
            be required for completing activities
    \end{enumerate}

### 2015-03-20 paper_30_measure.tex
more grammatical fixes updates to lists in the appendix

    \subsection{METRICS}
        A \textit{metric} can be defined as a means of telling a complete story
        for the purpose of improving something \cite{Klubeck2011}.  Metrics are
        frequently indirect measurements and
        are very common in the measurement of SDOs.  
        The following are some examples of metrics that can be collected 
        for an SDO. 
        \begin{itemize}
            \item SLOC - The number of Source Lines of Code 
                \nomenclature{SLOC}{Source Lines Of Code}
            \item NOM - The Number of Methods per class
                \nomenclature{NOM}{Number of Methods}
            \item Complexity - A numerical measure of the code complexity,
                some common examples are McCabe \cite{McCabe1976} and 
                Halstead \cite{Halstead1977}
            \item Design - The amount of coupling and cohesion present 
                in the software code
            \item Source Code Analysis - Tools that determine whether 
                code adheres to specified set of rules. Common 
                examples are PMD\footnote{PMD is a source code analysis product.  
                It is not an acronym.} and FindBugs$^{TM}$ \cite{PMD, Findbugs}.
        \end{itemize}
        All these metrics are beneficial, but none of them tell the story of the entire
        SDO.  Most of the metrics, as seen in the list above, for an SDO focus on 
        the source code and development phase. 
        Since metrics are indirect, it can be very difficult match SDO performance with
        a metric or series of metrics.  Metrics are great for tracking, but decision making
        based upon metrics alone is difficult.  That is why many of the other techniques
        build upon metrics to provide a more complete overall picture of an SDO. Metrics are great starting point, but more is needed to properly 
        evaluate performance.

@@

        Indicators can be used in just about every organizational
        setting from businesses to non-profit organizations. They
        are not unique to SDOs, and the exact indicators to track
        is very specific to the organization.  The indicators chosen
        by one organization might not be the same as the indicators
        chosen by another organization.  The following sections
        will explain the type of indicators in more detail and provide
        some examples for an SDO.

@@

        \subsubsection{KEY PERFORMANCE INDICATOR (KPI) FOR AN SDO}
            \textit{Key Performance Indicators} are performance measures
            focusing on critical aspects for current and future organizational
            success.  Notice, KPIs are not focused on historical performance,
            and they clearly indicate how to drastically increase performance.
            KPIs allow a team to monitor current performance and 
            quickly take action to correct future performance.
            KPIs cover a shorter time frame than KRIs.
            KPIs consist of the following 7 characteristics \cite{parmenter2010}.
            \begin{enumerate}
                \item Not financial
                \item Measured frequently (hourly, daily, weekly)
                \item Acted on by CEO\footnote{Chief Executive Officer} 
                    and/or upper-level management 
                    \nomenclature{CEO}{Chief Executive Officer}
                \item Clearly indicate the action required
                \item Tie responsibility to a particular team
                \item Have a significant impact
                \item Encourage appropriate action
            \end{enumerate}

            Antolic in \cite{Antolic2008} made one of the earliest attempts
            to identify and measure the KPIs for an SDO. Antolic's strategy
            focused around 7 KPIs.
            \begin{enumerate}
                \item Schedule adherence
                \item Assigned content adherence
                \item Cost adherence
                \item Fault slip through
                \item Trouble report closure rate
                \item Cost per defect
            \end{enumerate}
            However, according to the definition of KPI just presented,
            they are not really KPIs but instead KRIs.  That is because
            none of the 7 clearly indicate the action required to 
            improve the measure.  Also, it is unclear if improving any of
            the measures will drastically improve performance.

@@

        In 2010, David Parmenter \cite{parmenter2010} added 2 more
        characteristics to the balanced scorecard: employee satisfaction
        and environment/community.  This results in a total of 6 
        characteristics for the balanced scorecard.
        \begin{enumerate}
          \item Financial 
          \item Customer Focus
          \item Internal Process
          \item Learning and Growth
          \item Employee Satisfaction\footnote{\label{ft:bsc} Added 
          later by Parmenter \cite{parmenter2010}. }
          \item Environment/Community\textsuperscript{\ref{ft:bsc}}
        \end{enumerate}

        Balanced scorecards are great for easily displaying the 
        important information about
        an organization.  The downside is a balanced scorecard does not specify what
        exactly needs to be tracked. It can be very difficult to determine exactly
        what PIs, RIs, KRIs and/or KPIs to track in a balanced scorecard. 
        It just specifies 6 broad categories.
        It is also not specific to an SDO and 
        it does not produce a single number.  However, any new measurement
        technique for an organization should be compared with the balanced
        scorecard.

    \subsection{PROJECT MANAGEMENT MEASUREMENT}
    \label{sec:pm}
        A final strategy to measure an SDO is focused on the aspect of
        project management. Project management is the guidance
        applied to a project to ensure an effective and efficient
        completion.  Proper project management will ensure all steps
        of the SDLC
        continue to progress and all obstacles are handled
        in a timely fashion.  
        According to Putnam and Myers in \cite{Putnam2013}, 
        the 5 core measurements for managing software
        projects are:

        \begin{enumerate}
            \item \textbf{Quantity of function} usually measured in terms of size (such as source lines of code), that ultimately execute on the computer
            \item \textbf{Productivity} as expressed in terms of the functionality produced for the time and effort expended
            \item \textbf{Time} the duration of the project in calendar months
            \item \textbf{Effort} the amount of work expended in person-months
            \item \textbf{Reliability} as expressed in terms of defect rate (or its reciprocal, mean time to defect)
        \end{enumerate}

        A \textit{process productivity} number is calculated based entirely
        on aspects of the SDLC and the 5 core measurements.  It is a number
        targeted at project teams working on the SDLC.

>>>>

    \subsection{METRICS}
        A \textit{metric} can be defined as a means of telling a complete story
        for the purpose of improving something \cite{Klubeck2011}.  Metrics are
        frequently indirect measurements and
        are very common in the measurement of SDOs.  
        The following are some examples of metrics that can be collected 
        for an SDO. 
        \begin{itemize}
            \item SLOC - The number of Source Lines of Code 
                \nomenclature{SLOC}{Source Lines Of Code}
            \item NOM - The Number of Methods per class
                \nomenclature{NOM}{Number of Methods}
            \item Complexity - A numerical measure of the code complexity,
                some common examples are McCabe \cite{McCabe1976} and 
                Halstead \cite{Halstead1977}
            \item Design - The amount of coupling and cohesion present 
                in the software code
            \item Source Code Analysis - Tools that determine whether 
                code adheres to specified set of rules. Common 
                examples are PMD\footnote{PMD is a source code analysis product.  
                It is not an acronym.} and FindBugs$^{TM}$ \cite{PMD, Findbugs}.
        \end{itemize}
        All these metrics are beneficial, but none of them tell the story of the entire
        SDO.  Most of the metrics for an SDO, as seen in the list above, focus on 
        the source code and development phase. 
        Since metrics are indirect, it can be very difficult to match SDO performance with
        a metric or series of metrics.  Metrics are great for tracking, but decision making
        based upon metrics alone is difficult.  That is why many of the other techniques
        build upon metrics to provide a more complete overall picture of an SDO. Metrics are a great starting point, but more is needed to properly 
        evaluate performance.

@@

        Indicators can be used in just about every organizational
        setting from businesses to non-profit organizations. They
        are not unique to SDOs, and the exact indicators to track
        are very specific to the organization.  The indicators chosen
        by one organization might not be the same as the indicators
        chosen by another organization.  The following sections
        will explain the type of indicators in more detail and provide
        some examples for an SDO.

@@

        \subsubsection{KEY PERFORMANCE INDICATOR (KPI) FOR AN SDO}
            \textit{Key Performance Indicators} are performance measures
            focusing on critical aspects for current and future organizational
            success.  Notice, KPIs are not focused on historical performance,
            and they clearly indicate how to drastically increase performance.
            KPIs allow a team to monitor current performance and 
            quickly take action to correct future performance.
            KPIs cover a shorter time frame than KRIs.
            KPIs consist of the following seven characteristics \cite{parmenter2010}.
            \begin{enumerate}
                \item Not financial
                \item Measured frequently (hourly, daily, weekly)
                \item Acted on by CEO\footnote{Chief Executive Officer} 
                    and/or upper-level management 
                    \nomenclature{CEO}{Chief Executive Officer}
                \item Clearly indicate the action required
                \item Tie responsibility to a particular team
                \item Have a significant impact
                \item Encourage appropriate action
            \end{enumerate}

            Antolic in \cite{Antolic2008} made one of the earliest attempts
            to identify and measure the KPIs for an SDO. Antolic's strategy
            focused around six KPIs.
            \begin{enumerate}
                \item Schedule adherence
                \item Assigned content adherence
                \item Cost adherence
                \item Fault slip through
                \item Trouble report closure rate
                \item Cost per defect
            \end{enumerate}
            However, according to the definition of KPI just presented,
            they are not really KPIs but instead KRIs.  That is because
            none of the six clearly indicate the action required to 
            improve the measure.  Also, it is unclear if improving any of
            the measures will drastically improve performance.

@@

        In 2010, David Parmenter \cite{parmenter2010} added two more
        characteristics to the balanced scorecard: employee satisfaction
        and environment/community.  This results in a total of six 
        characteristics for the balanced scorecard.
        \begin{enumerate}
          \item Financial 
          \item Customer Focus
          \item Internal Process
          \item Learning and Growth
          \item Employee Satisfaction\footnote{\label{ft:bsc} Added 
          later by Parmenter \cite{parmenter2010}. }
          \item Environment/Community\textsuperscript{\ref{ft:bsc}}
        \end{enumerate}

        Balanced scorecards are great for easily displaying the 
        important information about
        an organization.  The downside is a balanced scorecard does not specify what
        exactly needs to be tracked. It can be very difficult to determine exactly
        what PIs, RIs, KRIs and/or KPIs to track in a balanced scorecard. 
        It specifies six broad categories.
        It is also not specific to an SDO and 
        it does not produce a single number.  However, any new measurement
        technique for an organization should be compared with the balanced
        scorecard.

    \subsection{PROJECT MANAGEMENT MEASUREMENT}
    \label{sec:pm}
        A final strategy to measure an SDO is focused on the aspect of
        project management. Project management is the guidance
        applied to a project to ensure an effective and efficient
        completion.  Proper project management will ensure all steps
        of the SDLC
        continue to progress and all obstacles are handled
        in a timely fashion.  
        According to Putnam and Myers in \cite{Putnam2013}, 
        the five core measurements for managing software
        projects are:

        \begin{enumerate}
            \item \textbf{Quantity of function} - usually measured in terms of size (such as source lines of code), that ultimately execute on the computer
            \item \textbf{Productivity} - as expressed in terms of the functionality produced for the time and effort expended
            \item \textbf{Time} - the duration of the project in calendar months
            \item \textbf{Effort} - the amount of work expended in person-months
            \item \textbf{Reliability} - as expressed in terms of defect rate (or its reciprocal, mean time to defect)
        \end{enumerate}

        A \textit{process productivity} number is calculated based entirely
        on aspects of the SDLC and the five core measurements.  It is a number
        targeted at project teams working on the SDLC.
